### 2024-04-07 message-from-committee.tex
2024 init commit

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 2022}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vspace{2em}
\thispagestyle{empty}

@@

%\end{flushright}
\begin{verbatim}

\Message2020{16}{uenchiest}{$2^6$}
\end{verbatim}

>>>>

{\sffamily
\begin{tabular}{ll}
\multirow{3}{*}{\includegraphics[width=1in]{ach.png}}\\
& \textbf{\Huge{SIGBOVIK 0x2024}} \\ &\\
& \LARGE{Message from the Organizing Committee} \\
&\\
\hline
\end{tabular}}
\vfill
\thispagestyle{empty}

@@

%\end{flushright}
%\begin{verbatim}
%\Message2020{16}{uenchiest}{$2^6$}
%\end{verbatim}

time is small.

brevity is the wit of soul.

SIGBOVIK 2024 was full of plusplusgood articles.

A.C., H.P., J.M., T.7, S.B., S.M., and H.Q.B. were actively involved in publication and organization.

thus marks the end of the proceedings for this year.

-the SIGBOVIK '24/7\\

\vfill
